EGGs are adhesive!

### 2025-03-13 calco/main.tex
minori

Notice that there is another functor $K: \EqHyp \to \Set$ sending $(E, V, C, s, t, q)$ to $C$, and a morphism $(h_E, h_V, h_C)$ to $h_C$. We  exploit it to compute limits and colimits in $\EqHyp$. In order to do so. A full proof of the following lemma can be found in \Cref{proof:comp}.

@@

	Now we have done, since by computing we have
\[\begin{split}
	y_1\circ a_3&= q'_4\circ p'_2=p'_3 \circ q'_3=y_1\circ m_3\circ q'_3\\
u_1\circ a_2&= q'_4\circ t'_2=t'_3 \circ q'_3=u_1\circ m_2\circ q'_2 
\end{split} \qquad \begin{split}
 	y_2\circ a_3&= d_3\circ q_3'=y_2\circ m_3\circ q'_3\\
u_2\circ a_2&= d_2\circ q_2'=u_2\circ m_2\circ q'_2
\end{split}\]	
%	And we have done.
\end{proof}

>>>>

Notice that there is another functor $K: \EqHyp \to \Set$ sending $(E, V, Q, s, t, q)$ to $Q$, and a morphism $(h_E, h_V, h_Q)$ to $h_Q$. We  exploit it to compute limits and colimits in $\EqHyp$. In order to do so. A full proof of the following lemma can be found in \Cref{proof:comp}.

@@

Computing we have
\[\begin{split}
	y_1\circ a_3&= q'_4\circ p'_2=p'_3 \circ q'_3=y_1\circ m_3\circ q'_3\\
u_1\circ a_2&= q'_4\circ t'_2=t'_3 \circ q'_3=u_1\circ m_2\circ q'_2 
\end{split} \qquad \begin{split}
 	y_2\circ a_3&= d_3\circ q_3'=y_2\circ m_3\circ q'_3\\
u_2\circ a_2&= d_2\circ q_2'=u_2\circ m_2\circ q'_2
\end{split}\]	
And we have done.
\end{proof}
